OCMu64: a solver for One-sided Crossing Minimization

### 2024-06-20 tex/description.tex
shrink text

\begin{description}
  \item[Graph simplification] We drop degree-$0$ vertices, merge identical
    vertices, and split the graph into \emph{independent} components when
    possible. We find an initial solution using local search that tries to move
    slices and optimally insert them, and re-label all nodes accordingly to make
    memory accesses more efficient.
  \item[Dominating pairs] We find all dominating pairs and store them. For the
    exact track we also find practical dominating pairs. Instances for the parameterized
    track are simple enough that the overhead was not worth it. Also for each
    tail we search for new `tail-local' practical dominating pairs. In each state, we only
    try vertices $u\in T$ not dominated by another $v\in T$.
  \item[Gluing] We use the greedy strategy \cref{greedy}. Our implementation
    of \cref{pg} contained a bug, so we did not use this. (Also benefits
    seemed limited.)
  \item[Tail cache] In each step, we search for the longest suffix of $T$ that
    has been seen before, and reuse (the lower bound on) its excess. We also
    cache the tail-local practical dominating pairs.
  \item[Optimal insert] Instead of simply appending $u$ to the end of $P$, we
    insert it in the optimal position.\footnote{The idea is simple, but the
    implementation is tricky because it interacts in complicated ways with
    the caching of results for each tail.}
\end{description}

>>>>

\begin{description}
  \item[Graph simplification] We drop degree-$0$ vertices, merge identical
    vertices, and split the graph into \emph{independent} components when
    possible. We find an initial solution using local search that tries to move
    slices and optimally insert them, and re-label all nodes accordingly to make
    memory accesses more efficient.
  \item[Fixed pairs] We find all strongly fixed pairs and store them. For the
    exact track we also find practical fixed pairs. Instances for the parameterized
    track are simple enough that the overhead was not worth it. Also for each
    tail we search for new `tail-local' practical fixed pairs. In each state, we only
    try vertices $u\in T$ not fixed by another $v\in T$.
  \item[Gluing] We use the greedy strategy of \cref{greedy}. Our implementation
    of \cref{pg} contained a bug, so we did not use this. (Also benefits
    seemed limited.)
  \item[Tail cache] In each step, we search for the longest suffix of $T$ that
    was seen before, and reuse (the lower bound on) its excess. We also
    cache the tail-local practical fixed pairs.
  \item[Optimal insert] Instead of simply appending $u$ to $P$, we
    insert it in the optimal position.\footnote{The idea is simple, but the
    implementation is tricky because it interacts in complicated ways with
    the caching of results for each tail.}
\end{description}
